String Constraints with Regex-Counting and String-Length Solved Efficiently

### 2023-05-09 2023-1-19/sections/implementation.tex
experiments

To answer Q2, we compare OSTRICH$^{\rm RECL}$ with its three variants, namely, OSTRICH$^{\rm RECL}_{\rm -SR}$, OSTRICH$^{\rm RECL}_{\rm -UA}$, OSTRICH$^{\rm RECL}_{\rm -SRUA}$, which remove size-reduction, under-approximation, and both from OSTRICH$^{\rm RECL}$ respectively. The experiment results can be found in Table~\ref{tab:results_heuristics}.
From Table~\ref{tab:results_heuristics}, we can see that adding size-reduction techniques help solve \zhilin{xxx} more instances, while adding under-approximation techniques help solve \zhilin{xxx} more instances, while adding both help solve \zhilin{xxx} more instances. Moreover, adding these techniques also decrease the average time spent in solving each instance considerably.

\begin{table}[ht]
\begin{center}
  \subimport{tables}{table_heuristic.tex}
\end{center}
  \caption{Experiment results for Q2}
  \label{tab:results_heuristics}
\end{table}

>>>>

To answer Q2, we compare OSTRICH$^{\rm RECL}$ with its three variants, namely, OSTRICH$^{\rm RECL}_{\rm -SR}$, OSTRICH$^{\rm RECL}_{\rm -UA}$, OSTRICH$^{\rm RECL}_{\rm -SRUA}$, which remove size-reduction, under-approximation, and both from OSTRICH$^{\rm RECL}$ respectively. The experiment results can be found in Table~\ref{tab:results_heuristics}.
From Table~\ref{tab:results_heuristics}, we can see that adding size-reduction techniques help solve \zhilin{xxx} more instances and reduce the average time per instance for \zhilin{xxx}/\%, while adding under-approximation techniques help solve \zhilin{xxx} more instances and reduce the average time per instance for \zhilin{xxx}/\%, while adding both help solve \zhilin{xxx} more instances and reduce the average time per instance for \zhilin{xxx}/\%. 
%Moreover, adding these techniques also decrease the average time spent in solving each instance considerably.

\begin{table}[ht]
\begin{center}
  \subimport{tables}{table_heuristic.tex}
\end{center}
  \caption{Experiment results for Q2, where the timeout period is 60 seconds}
  \label{tab:results_heuristics}
\end{table}
